A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-09 main.tex
Add e-mail.

Another important rule about a transition variable is 
that symbols with transition variables disappear 
when the empty transition $\epsilon$ is substituted to the transition variable.
The purpose of this rule is express \verb|run| without any special symbol.
In multistage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
In \LTP, \verb|run| is realized with application of the empty transition $\epsilon$.

@@

% CSP
CSP, cross-stage persistence, is an important feature of multistage calculus.
It enables us to embed value at an outer transition into an inner transition.
\red{inner / outer は適切か?}
$\%$ is dedicated to CSP in \LTP.
For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$

% Omitting Residualization

There is another important function called program residualization in \LTP.
It means that a generated code can be dumped into a file.
We can load the dumped file and run it.
The difficulty arises when program residualization is used with CSP.
Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.

@@

In this section, we present \LMD in detail. we will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context which take stages into account.
In the next section, we will discuss on properties of \LMD.

@@

\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies. Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures. This category encompasses both theoretical and implementation (also known as system descriptions) papers. In either case, submissions should clearly identify what has been accomplished and why it is significant. Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity. System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design. In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
\end{document}

>>>>

Another important rule about a transition variable is 
that symbols with transition variables disappear 
when the empty transition $\epsilon$ is substituted to the transition variable.
The purpose of this rule is express \verb|run| without any special symbol.
In multistage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
Therefore, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
In \LTP, \verb|run| is realized with application to the empty transition $\epsilon$.

@@

% CSP

CSP, cross-stage persistence, is an important feature of \LTP.
It enables us to embed value at an outer transition into an inner transition.
$\%$ is dedicated to CSP in \LTP.
For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
\red{inner / outer は適切か?}

% Omitting Residualization
% この段落は3章のM eのあとに、この制限の結果として...という形で入れる

% There is another important feature called program residualization in \LTP.
% It means that a generated code can be dumped into a file.
% We can load the dumped file and run it.
% The difficulty arises when program residualization is used with CSP.
% Transition variables are classified into two kinds in \LTP in order to deal with this difficulty.

@@

In this section, we present \LMD in detail. 
We will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context, which take stages into account.
In the next section, we will discuss on properties of \LMD.

@@

\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies. Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures. This category encompasses both theoretical and implementation (also known as system descriptions) papers. In either case, submissions should clearly identify what has been accomplished and why it is significant. Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity. System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design. In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
\blue{Review Process
APLAS 2019 will use a lightweight double-blind reviewing process. Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper. The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
To facilitate this process, submitted papers must adhere to the following:
Author names and institutions must be omitted and
References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try. Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas. For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure. Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would. For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
\end{document}
